---
title: "TidyTuesday1"
author: "Julia Frederick"
date: "10/3/2019"
output: html_document
---

### This week's TidyTuesday is on Pizza Places
Lets load in the data
```{r, load data}
pizza_jared <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_jared.csv")
pizza_barstool <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_barstool.csv")
pizza_datafiniti <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_datafiniti.csv")
```

### Examine the data
```{r, summary data}
summary(pizza_datafiniti)
```

### Load in the libraries needed
```{r,libraries}
library(tidyverse)
library(ggplot2)
library(magrittr)
library(dplyr)
```


### Visualize the data
How many pizza places are there per state
```{r, graph pizza and state}
#finding out how many places serve pizza per state
pizzastate <- pizza_datafiniti %>% group_by(province) %>% summarize(npizza = length(name))

#quick plot of pizza by state
ggplot(pizzastate, aes(x=province, y=npizza)) +
  geom_point()
summary(pizzastate)
which.max(pizzastate$npizza)
pizzastate$province[31]
```

### New York has a lot of pizza places!
It has 2640 pizza places - lets look more at those
```{r, subset newyork}
nypizza <- subset(pizza_datafiniti, province == "NY")
```

Some places appear to be duplicated, lets keep only those that are unique
```{r, finding all unique pizza places}
#number of times a place is listed
chain <- nypizza %>% group_by(name) %>% summarize(nlocations = length(latitude))
#joining previous table to current
nypizza %<>% left_join(.,chain)
#each address is only listed once now
unchain <- distinct(nypizza, address, .keep_all = TRUE)
```

Are they evenly distributed?
```{r}
NYcities <- unchain %>% group_by(city) %>% summarize(npp = length(latitude))
ggplot(NYcities) +
  geom_bar(aes(x=npp))
```

No, one city appears to have way more than the others
```{r}
which.max(NYcities$npp)
NYcities$city[92]
```

### New York City has the most, no surprise there.
The `pizza_barstool` dataset looks specifically at New York City so let's switch to there

```{r}
summary(pizza_barstool)
```

What is the average rating of a pizza place in NYC 
```{r}
summary(pizza_barstool$review_stats_dave_average_score)

ggplot(pizza_barstool) +
  geom_bar(aes(x=review_stats_dave_average_score)) +
  ggtitle("Distribution of pizza ratings in New York City") +
      theme(plot.title = element_text(lineheight = .8, face="bold")) +
  xlab("Average Review Rating from Dave") +
  ylab("Number of places with that score") +
  geom_vline(xintercept = 6.623, color = "red")
``` 

For those that are "Above Average" what is the price level?
```{r}
aboveavg <- subset(pizza_barstool, review_stats_dave_average_score >= 6.623)

ggplot(aboveavg) +
  geom_bar(aes(x=review_stats_dave_average_score)) +
  ggtitle("Distribution of ABOVE AVERAGE pizza ratings by\n price level in New York City") +
      theme(plot.title = element_text(lineheight = .8, face="bold")) + 
  facet_grid(.~price_level) +
  xlab("Average Review Rating from Dave") +
  ylab("Number of places with that score") 
```

  

